\documentclass[11pt,letterpaper,sans]{moderncv}

%%%%%%%%%%
% Themes %
%%%%%%%%%%

\moderncvstyle{banking}
\moderncvcolor{orange}


%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%

\usepackage[top=0.5in, left=0.75in, right=0.75in, bottom=0.5in]{geometry}


%%%%%%%%%%%%%%%%%
% Personal data %
%%%%%%%%%%%%%%%%%

% \firstname{Peter}
% \lastname{Zieske}
\name{Peter}{Zieske}
\address{7319 Willow Creek Drive}{Ypsilanti, MI 48197}
\mobile{+1~(734)~358~7208}
\email{pdz8@cornell.edu}
% \social[linkedin]{peter-zieske}
% \social[github]{pdz8}


%%%%%%%%%%
% Resume %
%%%%%%%%%%

\begin{document}

\makecvtitle

\section{Education}

\cventry{Aug 2014 - May 2015}{Master of Engineering}
{Cornell University, \mdseries College of Engineering}{Ithaca, NY}
{Computer Science, \textup{GPA: 4.052}}
{}
\medskip

\cventry{Aug 2011 - May 2014}{Bachelor of Science}
{Cornell University, \mdseries College of Engineering}{Ithaca, NY}
{Computer Science, \textup{GPA: 3.876}}
{}
\medskip

% \cventry{Sept 2007 - May 2011}{\upshape GPA: $\sim$ 4.2}
% {Lincoln Senior High School}{Ypsilanti, MI}
% {}
% {}

\section{Experience}

\cventry{Jan 2015 - May 2015}{Developer}
{CrowdVerity}{Ithaca, NY}
{}
{Worked with professor Emin G\"{u}n Sirer on M.Eng project \url{crowdverity.com}. CrowdVerity uses Ethereum to import facts from the real-world into the digital and block-chain domains. [Ethereum, Django]}
\medskip

\cventry{May 2014 - Aug 2014}{SDE Intern}
{Microsoft}{Redmond, WA}
{}
{Worked to enhance security and flexibility in Engineering Systems of Operating Systems Core. [C/C++]}
\medskip

\cventry{May 2013 - Aug 2013}{SDET Intern}
{Microsoft}{Redmond, WA}
{}
{Developed both traditional and randomized testing automation for the Email and Calendar team in Windows Phone. [C\#]}
\medskip

\cventry{Aug 2013 - May 2015}{Teaching Assistant}
{Cornell University}{Ithaca, NY}
{}
{Served on course staff for CS 3110 Data Structures and Functional Programming, CS 4820 Introduction to the Analysis of Algorithms ($\times$2), and CS 4410 Operating Systems. [OCaml, \LaTeX, Python, C]}
\medskip

\cventry{May 2013 - Aug 2013}{Developer}
{Pirates of the Stratosphere}{Ithaca, NY}
{}
{Worked in a 5 member interdisciplinary team to create a pirate-themed shooter. The game won in Cornell's 2013 GDIAC Showcase. [C\#]}
\medskip

% \cventry{Jan 2013 - May 2013}{Undergraduate Researcher}
% {Cornell University}{Ithaca, NY}
% {}
% {Explored the use of network flow algorithms in computer vision under Professor Ramin Zabih.}
% \medskip

\cventry{Sept 2011 - May 2013}{Developer}
{Violet Nano-Satellite Project Team}{Ithaca, NY}
{}
{Worked with the satellite's power board on the Command and Data Handling subsystem of the team. [C, Python]}
\medskip

\cventry{June 2012 - Aug 2013}{Independent}
{Windows Phone App Development}{Ypsilanti, MI}
{}
{Designed and developed 5 apps for Windows Phone 7 and 8 with total downloads exceeding 10k.  The most recent app \emph{Bus Alarm} placed first in Microsoft's 2013 Intern AppHack competition. [C\#]}
\medskip


% \cventry{June 2012 - August 2012}{Developer}
% {Mt. Olivet Cemetery Database}{Chelsea, MI}
% {}
% {Create a user-friendly management system for a cemetery near my hometown. [VBA]}
% \medskip

\section{Technical Skills}
\cvitem{Languages}{C\#, C/C++, Java, OCaml, Python, HTML/JavaScript/CSS, VBA, Matlab, Prolog, Perl}
\medskip
\cvitem{Tools}{SSH, \LaTeX, Git, Powershell, Unix, Visual Studio, Django, AngularJS}

\end{document}
